\Title

### 2023-05-29 source/tex/paper.tex
Correct free indices on eqtns 11.19* take 2.
In the previous commit I made the changes (on the free indices) in the sources but forgot to do so in the main paper.tex file. Now fixed. Finally. Sheesh.
Simplified installation, updated hybrid-latex tools
1. Non-trivial refactoring of the build/install scripts.
   This was both to tidy the file structure as well as to simplify the installation
   process. The default install is now as simple as "source SETPATHS; make install".
   Almost all install/build/test/clean actions are now controlled by Makefiles.

2. Updated cdbpreproc.py.
   The Cadabra

\pdfoutput=1% forces arxiv to use pdflatex
% --------------------------------------------------------------------------------------------
\def\Title{Riemann Normal Coordinate expansions using Cadabra.}
\def\Author{Leo Brewin}
% --------------------------------------------------------------------------------------------
\documentclass[a4paper,12pt]{article}
%
% biber will replace LaTeX accented characters like \'{e} with utf-8 characters.
% The utf-8 characters are written to the .bbl and this causes problems with pdflatex.
%    First  solution use: biber tutorial and \usepackage[latin1]{inputenc}
%    Second solution use: biber --decodecharsset=null tutorial
\usepackage[style=numeric, sorting=none, sortcites=true]{biblatex}
\addbibresource{bibdata.bib}
%
% \usepackage{showlabels}
% \usepackage{showkeys}
\usepackage{cdblatex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{paper}

@@

% ============================================================================================
\title{\Title}
\author{\Author\\[10pt]%
School of Mathematical Sciences\\%
Monash University, 3800\\%
Australia}
% \date{10-Nov-2008}% 1st version started
% \date{29-Nov-2008}% 1st version finished
% \date{10-Mar-2009}% 1st version to gr-qc
% \date{22-Mar-2009}% minor corrections to section 8.2
% \date{09-Jul-2009}% minor grammatical corrections in response to 1st referee
% \date{12-Aug-2009}% small corrections arising from proofs received from CQG
\date{12-Aug-2009 (v1)\\
      10-Dec-2019 (v2)}% major changes to correct errors in 4th and higher order terms,
                       % all code will be available on github
\reference{Preprint: arXiv:0903.2087\\[5pt]
           Journal: {\it Class.Quantum.Grav.} {\bf 26} 175017 (2009)}

@@

\BegNote{\bf\large Version 2}
The first version of this paper was written in 2009. This second version (written in 2019)
differs from the first in a number of important ways. First, the discussion on Cadabra has
been completely rewritten to account for the revised syntax introduced in the latest version
of Cadabra (itself updated in 2016)\footnote{The Cadabra results in this paper are based on
\CdbVersion}. Second, and more importantly, a significant computational error in the first
version (of this paper) has been corrected. Though the algorithms given in the first version
were correct their implementation in Cadabra (by this author) was incorrect. This lead to
errors first in the quartic and higher order terms in the generalised connections and then,
down the line, to computations built upon the generalised connections (e.g., the initial and
boundary value problem and the arc-length equations). The Cadabra codes have been corrected
and thoroughly cross-checked. A number of minor typographical errors have also been
corrected.
\EndNote

@@

First choose $s=0$ at $O$ and then write the Taylor series for $x^a(s)$ as
\[
x^a(s) = \left.x^a\right\vert_{s=0}
       + s \left.\frac{dx^a}{ds}\right\vert_{s=0}
       + \sum_{n=2}^\infty\> \frac{s^n}{n!}\left.\frac{d^nx^a}{ds^n}\right\vert_{s=0}
\]
The second and higher derivatives can be obtained by successive differentiation of the
geodesic equation leading to
\begin{equation}
x^a(s) = x^a + s {\Dot x}^a
       - \sum_{n=2}^\infty \frac{s^n}{n!}\Gamma^{a}{}_{i_1i_2i_3\cdots i_n}
                                         {\Dot x}^{i_1}
                                         {\Dot x}^{i_2}
                                         {\Dot x}^{i_3}\cdots
                                         {\Dot x}^{i_n}
\pglabel{eqn:SolIVP}
\end{equation}
where the $\Gamma^{a}{}_{i_1i_2i_3\cdots i_n}$, known as \emph{generalised connections},
are defined recursively by
\begin{equation}
\Gamma^{a}{}_{i_1i_2i_3\cdots i_n} = \Gamma^{a}{}_{(i_1i_2i_3\cdots i_{n-1},i_n)}
                                 - n \Gamma^{a}{}_{p(i_2i_3\cdots i_{n-1}}
                                     \Gamma^{p}{}_{i_1i_n)}
\pglabel{eqn:GenGam}
\end{equation}
Note that the use of round brackets $(...)$ denotes total symmetrisation over the included
indices (see Appendix A for more details).

@@

This problem has been discussed once before, in section (\ref{sub:CoordsBVP}). Using equation
\eqref{eqn:SolIVP} and the generalised connections from section (\ref{sec:GenGamma}) leads to
%
\begin{dmath*}x^{a}(s)
   = x^{a}
   + s \dotx^{a}
   + \frac{1}{24} s^2 {\Dot x}^b {\Dot x}^c \Bigl(\cdb{ivp42}\Bigr)
   + \frac{1}{12} s^3 {\Dot x}^b {\Dot x}^c {\Dot x}^d \cdb{ivp43}
   + \BigO{s^4,\eps^4}\end{dmath*}
%
% --------------------------------------------------------------------------------------------
\subsection{Geodesic boundary value problem}\label{sec:GeodesicBVP}

@@

% --------------------------------------------------------------------------------------------
\mysubsection{Symmetrised partial derivatives of the%
              Riemann curvature tensor.}\label{sub:partialRabcd}

@@

\begin{align}
   x^{d}(s) ={}& x^{d}
            + s {{\Dot x}^d}
            + \frac{s^2}{2!} {{\Dot x}^a} {{\Dot x}^b} A^{d}_{ab}
            + \frac{s^3}{3!} {{\Dot x}^a} {{\Dot x}^b} {{\Dot x}^c} A^{d}_{abc}
            + \frac{s^4}{4!} {{\Dot x}^a} {{\Dot x}^b} {{\Dot x}^c}
                                                       {{\Dot x}^d} A^{d}_{abce}\notag\\
           &+ \frac{s^5}{5!} {{\Dot x}^a} {{\Dot x}^b} {{\Dot x}^c} {{\Dot x}^d}
                                                       {{\Dot x}^e} A^{d}_{abcef}
            + \BigO{s^6,\eps^6}\tag{11.19}
\end{align}
\begin{dgroup*}
   \dMath{11.19a}{ 360 A^{d}_{ab} = \cdb{ivp62}}{eqn:ivp62}{\hfill}
   \dMath{11.19b}{ 360 A^{d}_{abc} = \cdb{ivp63}}{eqn:ivp63}{\hskip 0.5cm}
   \dMath{11.19c}{  90 A^{d}_{abce} = \cdb{ivp64}}{eqn:ivp64}{\hfill}
   \dMath{11.19d}{   3 A^{d}_{abcef} = \cdb{ivp65}}{eqn:ivp65}{\hfill}
\end{dgroup*}

>>>>

\pdfoutput=1% forces arxiv to use pdflatex
% --------------------------------------------------------------------------------------------
\def\Title{Riemann Normal Coordinate expansions using Cadabra.}
\def\Author{Leo Brewin}
% --------------------------------------------------------------------------------------------
\documentclass[a4paper,12pt]{article}
%
% biber will replace LaTeX accented characters like \'{e} with utf-8 characters.
% The utf-8 characters are written to the .bbl and this causes problems with pdflatex.
%    First  solution use: biber tutorial and \usepackage[latin1]{inputenc}
%    Second solution use: biber --decodecharsset=null file
\usepackage[style=numeric, sorting=none, sortcites=true]{biblatex}
\addbibresource{bibdata.bib}
%
% \usepackage{showlabels}
% \usepackage{showkeys}
\usepackage{cdblatex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{paper}

@@

% ============================================================================================
\title{\Title}
\author{\Author\\[10pt]%
School of Mathematical Sciences\\%
Monash University, 3800\\%
Australia}
% \date{10-Nov-2008}% 1st version started
% \date{29-Nov-2008}% 1st version finished
% \date{10-Mar-2009}% 1st version to gr-qc
% \date{22-Mar-2009}% minor corrections to section 8.2
% \date{09-Jul-2009}% minor grammatical corrections in response to 1st referee
% \date{12-Aug-2009}% small corrections arising from proofs received from CQG
\date{12-Aug-2009 (v1)\\
      10-Dec-2019 (v2)\\  % major changes to correct errors in 4th and higher order terms,
                          % all code will be available on github
       4-Nov-2022 (v3)\\  % corrected typos on lhs of eqtns 11.19a-d,
       1-Dec-2022 (v4)}   % corrected typo on equation (3.2) in section (3.1)
\reference{Preprint: arXiv:0903.2087\\[5pt]
           Journal: {\it Class.Quantum.Grav.} {\bf 26} 175017 (2009)}

@@

\bgroup
\BegNote{\bf Version 2}
\small%
The first version of this paper was written in 2009. This second version (written in 2019)
differs from the first in a number of important ways. First, the discussion on Cadabra has
been completely rewritten to account for the revised syntax introduced in the latest version
of Cadabra (itself updated in 2016)\footnote{The Cadabra results in this paper are based on
\CdbVersion}. Second, and more importantly, a significant computational error in the first
version (of this paper) has been corrected. Though the algorithms given in the first version
were correct their implementation in Cadabra (by this author) was incorrect. This lead to
errors first in the quartic and higher order terms in the generalised connections and then,
down the line, to computations built upon the generalised connections (e.g., the initial and
boundary value problem and the arc-length equations). The Cadabra codes have been corrected
and thoroughly cross-checked. A number of minor typographical errors have also been
corrected.
% \EndNote
\vskip 2pt

\BegNote{\bf Version 3}
\small%
This version corrects the indicies (and sign) of the left hand side of equations 11.19a-d.
This brings the arXiv version in line with the version on GitHub
\ \url{https://github.com/leo-brewin/riemann-normal-coords}.
% \EndNote
\vskip 2pt

\BegNote{\bf Version 4}
\small%
Equation (3.2) in Section 3.1 had a small error -- the coefficient in front of the $\Gamma \Gamma$
term should be $(n-1)$ rather than $n$. Other instances of equation (3.2) (in section 4 and 7)
were correct. This was a simple typographical error. All of the Cadabra results are unchanged.
\EndNote
\egroup

@@

First choose $s=0$ at $O$ and then write the Taylor series for $x^a(s)$ as
\[
x^a(s) = \left.x^a\right\vert_{s=0}
       + s \left.\frac{dx^a}{ds}\right\vert_{s=0}
       + \sum_{n=2}^\infty\> \frac{s^n}{n!}\left.\frac{d^nx^a}{ds^n}\right\vert_{s=0}
\]
The second and higher derivatives can be obtained by successive differentiation of the
geodesic equation leading to
\begin{equation}
x^a(s) = x^a + s {\Dot x}^a
       - \sum_{n=2}^\infty \frac{s^n}{n!}\Gamma^{a}{}_{i_1i_2i_3\cdots i_n}
                                         {\Dot x}^{i_1}
                                         {\Dot x}^{i_2}
                                         {\Dot x}^{i_3}\cdots
                                         {\Dot x}^{i_n}
\pglabel{eqn:SolIVP}
\end{equation}
where the $\Gamma^{a}{}_{i_1i_2i_3\cdots i_n}$, known as \emph{generalised connections},
are defined recursively by
\begin{equation}
  \Gamma^{a}{}_{i_1i_2i_3\cdots i_n}
= \Gamma^{a}{}_{(i_1i_2i_3\cdots i_{n-1},i_n)}
      - (n-1) \Gamma^{a}{}_{p(i_2i_3\cdots i_{n-1}}
              \Gamma^{p}{}_{i_1i_n)}
\pglabel{eqn:GenGam}
\end{equation}
Note that the use of round brackets $(...)$ denotes total symmetrisation over the included
indices (see Appendix A for more details).

@@

This problem has been discussed once before, in section (\ref{sub:CoordsBVP}). Using equation
\eqref{eqn:SolIVP} and the generalised connections from section (\ref{sec:GenGamma}) leads to
%
\begin{dmath*}x^{a}(s)
   = x^{a}
   + s \dotx^{a}
   + \frac{1}{24} s^2 {\Dot x}^b {\Dot x}^c \Bigl(\cdb{ivp42}\Bigr)
   + \frac{1}{12} s^3 {\Dot x}^b {\Dot x}^c {\Dot x}^d \bigl(\cdb{ivp43}\bigr)
   + \BigO{s^4,\eps^4}\end{dmath*}
%
% --------------------------------------------------------------------------------------------
\subsection{Geodesic boundary value problem}\label{sec:GeodesicBVP}

@@

% --------------------------------------------------------------------------------------------
\mysubsection{Symmetrised partial derivatives of the %
              Riemann curvature tensor.}\label{sub:partialRabcd}

@@

\begin{align}
   x^{a}(s) ={}& x^{a}
            + s {{\Dot x}^a}
            + \frac{s^2}{2!} {{\Dot x}^b} {{\Dot x}^c} A^{a}_{bc}
            + \frac{s^3}{3!} {{\Dot x}^b} {{\Dot x}^c} {{\Dot x}^d} A^{a}_{bcd}
            + \frac{s^4}{4!} {{\Dot x}^b} {{\Dot x}^c} {{\Dot x}^d}
                                                       {{\Dot x}^e} A^{a}_{bcde}\notag\\
           &+ \frac{s^5}{5!} {{\Dot x}^b} {{\Dot x}^c} {{\Dot x}^d}
                                                       {{\Dot x}^e}
                                                       {{\Dot x}^f} A^{a}_{bcdef}
            + \BigO{s^6,\eps^6}\tag{11.19}
\end{align}
\begin{dgroup*}
   \dMath{11.19a}{ 360 A^{a}_{bc} = \cdb{ivp62}}{eqn:ivp62}{\hfill}
   \dMath{11.19b}{ 360 A^{a}_{bcd} = \cdb{ivp63}}{eqn:ivp63}{\hskip 0.5cm}
   \dMath{11.19c}{  90 A^{a}_{bcde} = \cdb{ivp64}}{eqn:ivp64}{\hfill}
   \dMath{11.19d}{   3 A^{a}_{bcdef} = \cdb{ivp65}}{eqn:ivp65}{\hfill}
\end{dgroup*}
